Define Size classes

### 2022-11-27 supp/index.qmd
<edit index>

American Southeast, Caddo, NAGPRA, archaeoinformatics, museum studies, digital humanities, non-Western art history, geometric morphometrics, STEM, STEAM, ovoid biface, Jowell knife, Jowell knives, Jowell biface, lithics, oblique parallel flaking

@@

The pattern that emerges is one of differential retouch _intensity_, where the isometric retouch strategies of Caddo knappers from Millsap Cache articulate with a different reduction practice thought to be associated with locally abundant raw material (Kay County flint). This stands in contrast to the comparatively minimal retouch intensity of another group (Jowell Farm) where local raw materials were of poor quality and insufficient size, yielding a situation where it was necessary to import raw material from an extralocal source (Edwards chert).

>>>>

American Southeast, Caddo, NAGPRA, computational archaeology, archaeoinformatics, museum studies, digital humanities, non-Western art history, geometric morphometrics, STEM, STEAM, ovoid biface, Jowell knife, Jowell knives, Jowell biface, lithics, oblique parallel flaking

@@

The pattern that emerges is one of differential retouch _intensity_, where retouch strategies of Caddo knappers from Millsap Cache articulate with a reduction practice thought to be associated with locally abundant raw material (Kay County flint). This stands in contrast to the comparatively minimal retouch intensity of another group (Jowell Farm) where local raw materials were of poor quality and insufficient size, yielding a situation where it was necessary to import raw material from an extralocal source (Edwards chert).

### 2022-11-27 supp/sizeclass.qmd
<edit struc>
<edit index>

# Define size classes

@@

Landmark data were aligned to a global coordinate system [@RN8477;@RN7502;@RN11622;@RN11623;@RN11563], achieved through generalised Procrustes superimposition [@RN11138;@RN478;@RN1646] in R using the `geomorph` and `RRPP` packages [@RN1655;@RN11775;@RN11530;@RN1774;@RN9565]. Procrustes superimposition translates and rotates the coordinate data to allow for comparisons among objects, while also scaling each biface using unit-centroid size---the square root of the sum of squared distances from each landmark to the specimen’s centroid [@RN11139;@RN11140;@RN11564;@RN478]. The `geomorph` package uses a partial Procrustes superimposition that projects the aligned specimens into tangent space subsequent to alignment in preparation for the use of multivariate methods that assume linear space [@RN11141;@RN11142;@RN1646;@RN11563].

>>>>

---
title: "Define Size classes"
bibliography: [book.bib]
---

@@

Landmark data were aligned to a global coordinate system [@RN8477; @RN7502; @RN11622; @RN11623; @RN11563], achieved through generalised Procrustes superimposition [@RN11138; @RN478; @RN1646] in R using the `geomorph` and `RRPP` packages [@RN1655; @RN11775; @RN11530; @RN1774; @RN9565]. Procrustes superimposition translates and rotates the coordinate data to allow for comparisons among objects, while also scaling each biface using unit-centroid size---the square root of the sum of squared distances from each landmark to the specimen's centroid [@RN11139; @RN11140; @RN11564; @RN478]. The `geomorph` package uses a partial Procrustes superimposition that projects the aligned specimens into tangent space subsequent to alignment in preparation for the use of multivariate methods that assume linear space [@RN11141; @RN11142; @RN1646; @RN11563].
